What is happening on Twitter? A framework for student research projects with tweets

### 2020-06-01 Rmd/abstract.Rmd
fixed abstract

We describe methods for collecting tweets from Twitter. With these methods, we 
curate a large collection of tweets.
We present methods for social media event detection through text analysis of tweets. 
We describe our use of tweets in mentored undergraduate research. 
We also offer other directions for other text analysis of tweets.

>>>>

We present a framework for undergraduate research projects with Twitter data. 
Drawing on backward design principles, we share our learning objectives and
summative assessments. We draw on experiences mentoring two students during 
an academic year. To illustrate the value of Twitter as a data source, 
we detail methods for collecting and analyzing tweets. We conclude by emphasizing
how Twitter text analysis projects enable students to formulate 
original research questions, collect and analyze the needed data, and communicate
findings and their implications.

### 2020-06-01 Rmd/jse-special-issue-2020.Rmd
fixed capitalization
fixed abstract

---
title: "What is happening on Twitter? Tweet analysis and student research projects"
author: "Frederick J. Boehm and Bret M. Hanlon"
date: "June 15, 2020"
params:
  lastmod: !r lubridate::now()
bibliography: jse.bib
csl: american-statistical-association.csl
geometry: "left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm"
output: 
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: FALSE
    number_sections: TRUE
    includes:
      in_header: head.tex
  bookdown::word_document2:
    toc: FALSE
---

@@

@@

>>>>

---
title: "What is happening on Twitter? A framework for student research projects with tweets"
author: "Frederick J. Boehm and Bret M. Hanlon"
date: "June 15, 2020"
params:
  lastmod: !r lubridate::now()
bibliography: jse.bib
csl: american-statistical-association.csl
geometry: "left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm"
output: 
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: FALSE
    number_sections: TRUE
    includes:
      in_header: head.tex
  bookdown::word_document2:
    toc: FALSE
---

@@

Our mentoring in data science aligns with others' calls to reconsider training in statistics
and data science [@nolan2010computing;@carver2016guidelines]. @hicks2018guide argue for
incorporating three concepts into data science classes: computing, connecting and creating. 
They use the terms "connecting" and "creating" to describe the processes of applying 
quantitative methods to real data and real research questions and of research question 
formulation, respectively. Our tweet analysis projects offer students opportunities in all
three skills sets. Our students first formulated research questions, then collected and 
analyzed data to address the questions. Throughout the projects, students 
drew heavily on computing, both to acquire data and to analyze it.

@@

We include our R code in supplementary files.
